Privacy-preserving service provisioning using distributed networks

### 2023-01-17 paper/access.tex
update protocol steps

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

We propose a protocol for anonymously provisioning services that require the delivery of physical materials. A service provider employing our protocol can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Privacy-preserving cryptocurrency, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Content-addressable peer-to-peer storage network to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service, exchanges his materials and cryptocurrencies with the SP for the result of the service.

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized TTP, but uses decentralized blockchain and
distributed content-addressable storage network.

@@

\item TTP-less: 
our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of dispute the centralized justice is involved (the justice decentralization is discussed in section ~\ref{sec:discussion}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above using blockchain technology. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict
between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}.

Nevertheless, the blockchain paradigm has its limitations. Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.

@@

Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:discussion}.

@@

\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment1.pdf}
  \end{center}
\end{figure*}
\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{experiment2.pdf}
  \end{center}
\end{figure*}

\begin{description}
  \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
The customer's private key must be downloaded and provided later for the decryption of the results.

@@

\end{description}

@@

\subsection{Justice}\label{justice}

@@

The possible directions for mitigation of such issues are to either (i) replace justice with decentralized autonomous organizations (DAO) like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022}, or Aragon Court\footnote{https://aragon.org/aragon-court}; or (ii) make it infeasible to provide incorrect results.

@@

\begin{itemize}
\item Agreeable path:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{1, c, n} = \sbullet}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
  \item
    \(\operatorname{\sigma_{1, s, n} = \sbullet}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
  \item
    \(\operatorname{\sigma_{1, s, d} = \sbullet}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \sbullet}\).
\item
  The SP can do nothing and always ends up in the non-disadvantaged position.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{2, c, n} = \sbullet}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
  \item
    \(\operatorname{\sigma_{2, s, n} = \sbullet}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP didn't receive the payment on time.
  \item
    \(\operatorname{\sigma_{2, s, d} = \sbullet}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to publish correct $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item The customer can do nothing and always ends up in a non-disadvantaged position.
\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \sbullet}\).

@@

  \item
    $\operatorname{\sigma_{3, c, n} = \sbullet}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
  \item
    $\operatorname{\sigma_{3, s, n} = \sbullet}$, the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    $\operatorname{\sigma_{3, c, d} = -}$, the customer loses the case as the SP didn't receive the payment on time.
  \item
    $\operatorname{\sigma_{3, s, d} = \sbullet}$, the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{n}} = \sbullet}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
  \item
    \(\operatorname{\sigma_{3, s, \overline{n}} = \sbullet}\), the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to do anything before the payment is made.
  \item
    \(\operatorname{\sigma_{3, s, \overline{d}} = \sbullet}\), the SP wins the case and ends up in the neutral position.
  \end{itemize}
\end{itemize}

@@

\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \sbullet}\).
\item The SP can do nothing and always ends up in a non-disadvantaged position.
\end{itemize}

@@

  \begin{itemize}
  \item
    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
  \item
    \(\operatorname{\sigma_{2, s, d} = +}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{2, c, \overline{n}} = \sbullet}\), the customer ends up in the neutral position as he did not spend his funds.
  \item
    \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
  \item
    \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\), the SP is not charged to justice due to a lack of proof.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
\item
  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \sbullet}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \sbullet}\).
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
  \item
    \(\operatorname{\sigma_{3, s, d} = +}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \sbullet}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
  \item
    \(\operatorname{\sigma_{4, s, d} = +}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in a neutral position. 
  \item
    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \sbullet}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position. 
  \item
    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
  \(\operatorname{\sigma_{5, c, \overline{d}} = \sbullet}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \sbullet}\).
\item
  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \sbullet}\).
\item
  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
\end{itemize}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}

\newcommand\neutral[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}

\newcommand{\plus}{+}
\newcommand{\minus}{-}

\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

@@

% We observe
We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.

% Therefore we propose
We propose a protocol for anonymously provisioning services that require the delivery of physical materials. A service provider employing our protocol can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
    \item Content-addressable decentralised storage network (like IPFS) to anonymously provide results to customers. 
    \item Provable storage network (like Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service.
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on centralized TTP, but uses decentralized blockchain and
distributed content-addressable storage network.

@@

\item TTP-less: 
our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:justice}.
\item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
\end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all five properties stated above. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

@@

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}. Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}. However, the blockchain paradigm has its limitations.

Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.

@@

Possible directions toward semi-autonomous decentralized resolution system are discussed in Section~\ref{sec:decentralised-justice}.

@@

\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment1.pdf}
  \end{center}
\end{figure*}
\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{anonser-experiment2.pdf}
  \end{center}
\end{figure*}

\begin{enumerate}
  \setcounter{enumi}{0}
  \item[0.] The protocol starts with the customer opening the webapp and creating new provision. 
The app generates random ECDSA (secp256k1) customer's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the customer's public key. 
The customer's private key must be downloaded and provided later for the decryption of the results.

@@

\end{enumerate}

@@

\subsection{Justice}\label{sec:decentralised-justice}

@@

The possible directions for mitigation of such issues are to either (i) replace local justice with Online Dispute Resolution systems like proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other blockchain dispute resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

@@

\begin{itemize}
\item Agreeable path:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{1, c, n} = \neutral}\), the customer has risked its materials but has not paid for the transaction, so we assume he is in the neutral position \footnote{One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.}.
  \item
    \(\operatorname{\sigma_{1, s, n} = \neutral}\), the SP is in a neutral position as she did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{1, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe.
  \item
    \(\operatorname{\sigma_{1, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{1, c, n} = \neutral}\).
\item
  The SP can do nothing and always ends up in the non-disadvantaged position.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{2, c, n} = \neutral}\), the customer remains in the neutral position as the PoD allows him to pay for the transaction but does not obligate him to anything.
  \item
    \(\operatorname{\sigma_{2, s, n} = \neutral}\), the SP is in a neutral position because the package has not brought her any value and she did not put any effort to provide the service yet
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP didn't receive the payment on time.
  \item
    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer remains in the neutral position as he is not obligated agree with the incorrect $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP is in a neutral position as she did not put any effort to provide the service, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to publish correct $\mathrm{PoD}$.
  \item
    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\item The customer can do nothing and always ends up in a non-disadvantaged position.
\item The SP can follow the protocol ends up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = \neutral}\).

@@

  \item
    $\operatorname{\sigma_{3, c, n} = \neutral}$, the customer has the opportunity to pay for the transaction, but since he didn't put any effort, he is in the neutral position.
  \item
    $\operatorname{\sigma_{3, s, n} = \neutral}$, the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    $\operatorname{\sigma_{3, c, d} = -}$, the customer loses the case as the SP didn't receive the payment on time.
  \item
    $\operatorname{\sigma_{3, s, d} = \neutral}$, the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{n}} = \neutral}\), the customer can not follow the protocol but since he didn't put any efford he is in the neutral position.
  \item
    \(\operatorname{\sigma_{3, s, \overline{n}} = \neutral}\), the SP position has not changed.
  \end{itemize}
\item
  Starts a dispute:

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{d}} = -}\), the customer loses the case as the SP is not obligated to do anything before the payment is made.
  \item
    \(\operatorname{\sigma_{3, s, \overline{d}} = \neutral}\), the SP wins the case and ends up in the neutral position.
  \end{itemize}
\end{itemize}

@@

\item The customer can follow the protocol to the non-disadvantaged position \(\operatorname{\sigma_{3, c, n} = \neutral}\).
\item The SP can do nothing and always ends up in a non-disadvantaged position.
\end{itemize}

@@

  \begin{itemize}
  \item
    \(\operatorname{\sigma_{2, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision before the deadline.
  \item
    \(\operatorname{\sigma_{2, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item
  Following protocol:
  \begin{itemize}
  \item
    \(\operatorname{\sigma_{2, c, \overline{n}} = \neutral}\), the customer ends up in the neutral position as he did not spend his funds.
  \item
    \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), the SP ends up in a neutral position as he did not receive the payment, nor spent his resources.
  \end{itemize}
\item
  Starting a dispute:

@@

  \item
    \(\operatorname{\sigma_{2, c, \overline{d}} = -}\), the customer loses the case as he can not prove the payment before the time limit.
  \item
    \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\), the SP is not charged to justice due to a lack of proof.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can move the protocol forward to step 3, where if the SP follows the protocol then the customer can push the protocol forward up to the last termination step \(\operatorname{\sigma_{7, c, n} = +}\), otherwise if at any step the SP does not follow the protocol the customer can start a dispute which terminates the protocol at the non-disadvantaged position, i.e., \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
\item
  The SP can do nothing and end up in the non-disadvantaged position \(\operatorname{\sigma_{2, s, n} = +}\), \(\operatorname{\sigma_{2, s, d} = +}\), \(\operatorname{\sigma_{2, s, \overline{n}} = \neutral}\), \(\operatorname{\sigma_{2, s, \overline{d}} = \neutral}\).
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, d} = -}\), the customer loses the case as the SP has still the opportunity to publish proof of provision within the timeframe. 
  \item
    \(\operatorname{\sigma_{3, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{3, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{3, c, \overline{d}} = \neutral}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{3, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{3, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{4, c, d} = -}\), the customer loses the case as the SP has still an opportunity to publish proof of provision within the timeframe. 
  \item
    \(\operatorname{\sigma_{4, s, d} = \neutral}\), the SP win the case for the same reason.
  \end{itemize}
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in a neutral position. 
  \item
    \(\operatorname{\sigma_{4, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol, which will ultimately put him in an advantaged position \(\operatorname{\sigma_{7, c, n} = +}\), or in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position \(\operatorname{\sigma_{4, c, \overline{d}} = \neutral}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{4, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{4, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position. 
  \item
    \(\operatorname{\sigma_{5, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position. 
  \end{itemize}
\end{itemize}

@@

\item
  The customer can do nothing if the SP follows the protocol because it will ultimately put him in the advantaged position \(\operatorname{\sigma_{7, c, n} = +}\); otherwise, in case of the SP not following the protocol, the customer can start a dispute and terminate in the non-disadvantaged position.
  \(\operatorname{\sigma_{5, c, \overline{d}} = \neutral}\).
\item
  The SP can follow the protocol and move to the non-disadvantaged position \(\operatorname{\sigma_{5, s, n} = +}\), or not follow the protocol and also end up at the non-disadvantaged position \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), but the second option puts him at risk of terminating the protocol at \(\operatorname{\sigma_{5, s, \overline{n}} = +}\), if the customer is rational and starts a dispute.
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{6, s, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the position \(\operatorname{\sigma_{6, c, n} = -}\), which lets him move the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{6, c, \overline{d}} = \neutral}\).
\item
  The SP can do nothing and end up in a non-disadvantaged position \(\operatorname{\sigma_{6, s, n} = +}\), or \(\operatorname{\sigma_{6, s, \overline{n}} = +}\).
\end{itemize}

@@

  \item
    \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\), the customer wins the case and ends up in the neutral position.
  \item
    \(\operatorname{\sigma_{7, c, \overline{d}} = -}\), the SP loses the case and ends up in the disadvantaged position.
  \end{itemize}
\end{itemize}

@@

\item
  The customer can follow the protocol to the non-disadvantaged termination position \(\operatorname{\sigma_{7, c, n} = +}\), or in case the SP has not followed the protocol start a dispute and win the case \(\operatorname{\sigma_{7, c, \overline{d}} = \neutral}\).
\item
  The SP can do nothing and ends up in the non-disadvantaged position \(\operatorname{\sigma_{7, s, n} = +}\).
\end{itemize}

% \section{Appendix B: Smart contract code}\label{appendix-b-smart-contract-code}

% \input{solidity-highlighting.tex}
% \begin{lstlisting}[language=Solidity]
% // SPDX-License-Identifier: MIT
% pragma solidity >=0.4.22 <0.9.0;

% contract AnonSer {
%     struct Provision {
%         uint256 issueTime;
%         uint256 paymentDeadlineTime;
%         uint256 provisionDeadlineTime;
%         bool paidInCash;
%         string paymentAddress;
%         string cid;
%         bool exist;
%         uint256 dealId;
%         string minerId;
%     }

%     mapping(bytes => mapping(bytes32 => Provision)) public provisions;

%     address private _owner;

%     event ProofOfDelivery(
%         bytes indexed clientPubKey,
%         bytes32 indexed provisionId,
%         uint256 issueTime,
%         uint256 paymentDeadlineTime,
%         uint256 provisionDeadlineTime,
%         bool paidInCash,
%         string paymentAddress
%     );

%     constructor() {
%         _owner = msg.sender;
%     }

%     modifier onlyOwner() {
%         require(
%             _owner == msg.sender,
%             "Ownership Assertion: Caller of the function is not the owner."
%         );
%         _;
%     }
